---
title: "Graphical Analysis"
author: "Saif Ansari"
date: "August 8, 2016"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Graphical Analysis

I made up most of the data used in this project, they're both in my Git repository (linked in the asignment.) I also had to look up the syntax quite a bit at ggplot2.org and I also looked at a few articles on r-bloggers.com for graph use.

```{r}
#install("ggplot2")
library(ggplot2)
```

## Histogram

This imports the data, and sets up the graph, which is then illustrated below.

```{r}
sales <- read.csv(file="sales2.csv",header=TRUE,sep=",")

HistogramPlot = ggplot(data=sales, aes(sales$GoalsAttained))
HistogramPlot = HistogramPlot + geom_histogram(bins=20,col="black",fill="gray")
HistogramPlot = HistogramPlot + labs(x="Salespeople", y="Count")
HistogramPlot = HistogramPlot + labs(title="Histogram for Goals achieved during a month")

```
```{r echo=FALSE}
HistogramPlot
```

## Box Plot

Reading in some data to plot.

```{r}
sales <- read.csv(file="sales4.csv",header=TRUE,sep=",")

BoxPlot = ggplot(data=sales, aes(sales$Price,sales$Profit))
BoxPlot = BoxPlot + geom_boxplot() 
BoxPlot = BoxPlot + labs(x="Price", y="Profit")
BoxPlot = BoxPlot +labs(title="Box plot for Cost vs Price")
```
```{r echo=FALSE}
BoxPlot
```

## Scatter Plot

Using data from the above table to plot.

```{r}
ScatterPlot = ggplot(data=sales, aes(Price,Profit))
ScatterPlot = ScatterPlot + geom_point(aes(color = ProfitPerUnit))
ScatterPlot = ScatterPlot + labs(title="Scatterplot of Price and Profit as well as Profit Per unit")
```
```{r echo=FALSE}
ScatterPlot
```